Portal Forecast

### 2018-02-14 index.Rmd
add brief intro blurb

>>>>

Welcome to Portal Forecasting! This is a website run by the [Weecology](http://weecology.org/) group, a group of interdisciplinary ecologists at the [University of Florida](http://www.wec.ufl.edu/). On this website, you'll find information about our ongoing efforts to forecast ecological systems from time series. Specifically, we are using a times series of rodent abundances from [The Portal project](http://portal.weecology.org/), a long-term experimental monitoring project in desert ecology. Enjoy!
